Naming Anonymous JavaScript Functions

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
abstract/conclusion discussion

\begin{abstract}
Understanding JavaScript code due to its dynamic, weakly-typed nature is complicated. Developers usually comprehend JavaScript programs by running them and examining their elements at runtime. However, understanding concrete values, particularly user-defined and function objects, is not always straightforward. Function names can aid in this regard; they can appear as the constructor name in object representation or as the function identifier in call-stack. Based on our analysis over ten famous JavaScript projects, unfortunately only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place. As a solution to this problem, we propose an automated approach based on local source code analysis for naming nameless JavaScript functions. We applied our approach on several JavaScript projects and the results are very promising.
\end{abstract}

@@

\section{Special Cases}
Given that our goals trade precision for rapid recognition, our names are not unique or perfectly tuned to every developer's need. We also leave some cases anonymous. We add  few special cases to our algorithm to patch over these issues.

\subsection{Similar Function Names in a File}
It is conceivable, that function bodies are named with the same names in a file. It can happen in different situations. One of the common cases is the two different function bodies may assign to a property based on a condition (e.g., the browser). For these cases we add a dollar sign and an index to the similar function names. For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.

@@

\begin{table*}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
  \hline
   Project       & Anonymous &  FBUG NoName   & NoName   & NoShortName &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
  \hline 
   Closure       & 8987      &   312(3\%)     & 10       &  51         &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
  \hline 
   DoJo          & 15866     &   3362(2\%)    & 390      &  528        &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
  \hline 
   ExtJS         & 36533     &   1543(4\%)    & 231      &  631        &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
  \hline 
   Firebug       & 3018      &   167(5\%)     & 10       &  14         &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
  \hline 
   jQuery        & 399       &   95(24\%)     & 8        &  9          &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
  \hline 
   MochiKit      & 1829      &   202(11\%)    & 16       &  59         &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
  \hline 
   MooTools      & 618       &   121(19\%)    & 18       &  30         &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
  \hline 
   Prototype     & 442       &   125(28\%)    & 19       &  24         &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
  \hline  
   Scriptaculous & 884       &   195(22\%)    & 19       &  25         &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
  \hline    
   YUI           & 21424     &   3317(15\%)   & 15       &  212        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
  \hline 
   All           & 90000     &   9439(10\%)   & 736(1\%) &  1583(2\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   &                &          \\ 
  \hline       
  \end{tabular}
  }
 \label{evaluation} 
\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longest length of produced names for each project.}
\end{table*}

\section{evaluation}
The purpose of our evaluation is to answer the follwing questions: 1) How effective is the approach in naming anonymous functions? 2)How the algorithm  improves the current approaches used in available debuggers for inferring anonymous function names? 3) Are the proposed names are unique to be used as identifiers or conversely what portion of proposed names are duplicated? 4) Are the proposed names appropriate for user interface presentation?

We compared our results to Firebug naming output. Firebug does not use a parser for naming functions, it instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name. Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases. First column in Table~\ref{evaluation} contains the number of anonymous functions in each project. The second column shows the number of functions remained anonymous in Firebug. About 10 percent of anonymous functions still remained nameless in Firebug. The third column contains the number of functions which remained nameless after applying the static function object consumption algorithm. The numbers show that the algorihtm names more than 99 percent of anonymous functions. The next column shows how many of functions are named by do not have a short name (i.e., they are named only by their context names).

The fifth and sixth columns compare Firebug names to short names. In 15 percent of cases the short name is the same as firbug name. The next column shows the number of functions which their short name does not equals to Firebug name but ends with it. It means that short names contain more information (e.g., the function class name or parent object name) than Firebug names in 47 percent of cases.

@@

\subsection{Manual Check}
%namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
%commonjs requriejs, ...
%the function name not very long like google chrome  xxxx.yyy.zzz

@@

\section{Disucussion}

\subsection{ {\texttt .displayName} }
The ultimate fallback for function names is to allow the developer to specify them manually. For applicaiton developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.

\subsection{Limitations}
%some long names
%"this" in names

@@

\section{Conclusion}
We highlighted the problem of anonymous functions in JavaScript. We studied 10 famous JavaScript projects source code. From
our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
values and functions in the call-stack.

>>>>

\begin{abstract}
JavaScript developers create and call functions; they use functions to construct objects. JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and object representations. However, developers need not specify names for functions.  
 Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
By studying examples from these JavaScript projects, we propose Static Function-Object Consumption, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions.  We applied our approach to these same JavaScript projects and the results are very promising.
\end{abstract}

@@

@@

\begin{table*}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
  \hline
   Project       & Anonymous &  FBUG NoName   & NoName   & NoShortName &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
  \hline 
   Closure       & 8987      &   312(3\%)     & 10       &  51         &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
  \hline 
   DoJo          & 15866     &   3362(2\%)    & 390      &  528        &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
  \hline 
   ExtJS         & 36533     &   1543(4\%)    & 231      &  631        &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
  \hline 
   Firebug       & 3018      &   167(5\%)     & 10       &  14         &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
  \hline 
   jQuery        & 399       &   95(24\%)     & 8        &  9          &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
  \hline 
   MochiKit      & 1829      &   202(11\%)    & 16       &  59         &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
  \hline 
   MooTools      & 618       &   121(19\%)    & 18       &  30         &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
  \hline 
   Prototype     & 442       &   125(28\%)    & 19       &  24         &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
  \hline  
   Scriptaculous & 884       &   195(22\%)    & 19       &  25         &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
  \hline    
   YUI           & 21424     &   3317(15\%)   & 15       &  212        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
  \hline 
   All           & 90000     &   9439(10\%)   & 736(1\%) &  1583(2\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   &                &          \\ 
  \hline       
  \end{tabular}
  }
 \label{evaluation} 
\caption{Results of Function Object Consumption. The rows are the projects listed in Appendix 1. First column in  contains the number of anonymous functions in each project. The second column shows the number of functions Firebug could not name. The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm;  and the fourth column is the number with only a name for enclosing scopes. The fifth column give the number of times a FOC function name appears twice in a file and sixth and seventh columns give the average and longest name character counts respectively. The last columns have two entries divided by a slash, the first is the local name and the second is the full name.} 
\end{table*}

\section{Evaluation}
The purpose of our evaluation is to answer the following questions: 1) How effective is the approach in naming anonymous functions? 2) How the algorithm  improves the current approaches used in available debuggers for inferring anonymous function names? 3) Are the proposed names are unique to be used as identifiers or conversely what portion of proposed names are duplicated? 4) Are the proposed names appropriate for user interface presentation?

In Table~\ref{evaluation} We compared our results to Firebug's naming output for each of the 10 projects used previously and listed in Appendix 1. Firebug does not use a parser for naming functions. It instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name  (a function called {\small \texttt{guessFunctionName()}}). Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases. About 10 percent of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).The numbers show that the algorithm names more than 99 percent of the anonymous functions.

@@

%\subsection{Manual Check}
%namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
%commonjs requriejs, ...
%the function name not very long like google chrome  xxxx.yyy.zzz

@@

\section{Discussion}
Overall the Function-Object Consumption approach dramatically improves reduces the number of functions that a development tool cannot name for a developer.  By looking at the examples and comparing the algorithms, the names selected by FOC will be the same as the one's selected by  Firebug's {\small \texttt{guessFunctionName()}} when that function gives reasonable results. In other cases FOC will give a more useful name including many cases where the current Firebug approach fails.

There is room for improvements. The heuristic elements of the naming solution need to be tuned based on more experience.  Given that our goals trade precision for rapid recognition, our names are not unique. We also leave some cases anonymous which need further investigation.

\subsection{Similar Function Names in a File}
In some cases function bodies are named with the same names in a file. It can happen in different situations. One of the common cases is the two different function bodies may assign to a property based on a condition (e.g., the browser). For these cases we add a dollar sign and an index to the similar function names. For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.

\subsection{ {\texttt .displayName} }
The ultimate fallback for function names is to allow the developer to specify them manually. For application developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.

%\subsection{Limitations}
%some long names
%"this" in names

@@

\section{Conclusion}
Our contributions in this paper include an empirical study of the extent of anonymous functions in JavaScript libraries, categorization of those functions to understand the potential for automatic naming, an practical algorithm based on the empirical study, and its evaluation.   We believe our results can be applied directly in existing JavaScript development tools to give immediate benefit to developers and they provide a basis for future improvements.
